Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-12-01 paper/main.tex
reworking sheaf diagram

We model data as the sheaf $\sheafc({\dtotalc}): \mathcal{\dbasec}^{op} \textcolor{sheaf}{\rightarrow} \setc$. The objects of \textbf{Set} in this sheaf are the sets of sections introduced in \autoref{eq:related-work:continuity:sections} and the morphisms are the inclusion maps in \autoref{eq:related-work:continuity:presheaf}. 
\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \cgamma{\opensetc_i}{\dtotalc} \in Ob(\setc) & \\
{} \arrow[rr, "\dfuncc", Rightarrow, pos=.3, shorten <=3.5em, shorten >=8.85em, color=action] & & {} \\
    & \opensetc_i \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \arrow[uu, "\sheafc(\dtotalc)", bend left, shift left = 10.5, color=sheaf] \arrow[uu, "\sheafc(\dtotalc)"', bend right, shift left=10.5, color=sheaf] &   
\end{tikzcd}
\end{equation}
The map $\dfunc: \sheaf(\dtotal) \rightarrow \sheaf(\dtotal)$ is any arbitrary morphism between sheaf functors $\sheaf(\dtotal)$. Following from \autoref{eq:related-work:equivariance:natural-transform}, \dfunc\ is a natural transform, which means all inclusions $\iota, \iota^*$ are preserved as part of any $\dfunc$ transformation.

>>>>

We model data as the sheaf  $\sheafc({\dtotalc}): \mathcal{\dbasec}^{op} \textcolor{sheaf}{\rightarrow} \setc$.
\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \cgamma{\opensetc_i}{\dtotalc} \in Ob(\setc) & \\
    {} & & {} \\
    & \opensetc_i \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \arrow[uu, "\sheafc(\dtotalc)", shift left = 10.5, color=sheaf] &   
\end{tikzcd}
\end{equation}

The objects of \textbf{Set} in this sheaf are the sets of sections $\Gamma(\dbase, \dtotal)$ introduced in \autoref{eq:related-work:continuity:sections} and the morphisms are the inclusion maps $(\iota, \iota^*)$ introduced in \autoref{eq:related-work:continuity:presheaf}.

\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \cgamma{\opensetc_i}{\dtotalc} \in Ob(\setc) & \\
{} \arrow[rr, "\dfuncc", Rightarrow, pos=.3, shorten <=3.5em, shorten >=8.85em, color=action] & & {} \\
    & \opensetc_i \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \arrow[uu, "\sheafc(\dtotalc)", bend left, shift left = 10.5, color=sheaf] \arrow[uu, "\sheafc(\dtotalc)"', bend right, shift left=10.5, color=sheaf] &   
\end{tikzcd}
\end{equation}

The map $\dfunc: \sheaf(\dtotal) \rightarrow \sheaf(\dtotal)$ is any arbitrary morphism between sheaf functors $\sheaf(\dtotal)$. Following from \autoref{eq:related-work:equivariance:natural-transform}, \dfunc\ is a natural transform, which means all inclusions $\iota, \iota^*$ are preserved as part of any $\dfunc$ transformation.
